Processing of visual and non-visual naturalistic spatial information in the "parahippocampal place area"

### 2021-02-23 paper/main.tex
preprocessing: make difference between analyses and (raw) data clearer
restructure and rephrase annotation of cuts (!= movie frame content)

% data sources
% https://github.com/psychoinformatics-de/studyforrest-data-aligned/tree/master/code
% https://github.com/psychoinformatics-de/studyforrest-data-templatetransforms}
All analyses presented here are based on previously published fMRI data
(\url{https://github.com/psychoinformatics-de/studyforrest-data-aligned}).
Of those 15 participants in the studyforrest dataset that took
part in all three experiments,
% exclusion of VP 10
data of one participant were dropped to due to invalid distortion correction
during scanning of the audio-description stimulus.
Data were previously corrected for motion, aligned with and re-sliced onto a
participant-specific BOLD template image \citep{sengupta2016extension}
(uniform spatial resolution of \unit[2.5$\times$2.5$\times$2.5]{mm} for both
audio-description and movie data).
% preprocessing intro
Preprocessing was performed by FEAT v6.00 (FMRI Expert Analysis Tool;
\citep{woolrich2001autocorr}) as shipped with
FSL v5.0.9 (\href{https://www.fmrib.ox.ac.uk/fsl}{FMRIB's Software Library};
\citep{smith2004fsl}) on a computer-cluster running
\href{http://neuro.debian.net}{NeuroDebian} \citep{halchenko2012open}.

@@

% traditionally
In contrast to stimuli designed to trigger a perceptual process of interest,
while controlling for confounding variables (e.g., color and luminance),
% our approach: annotation and regressors
naturalistic stimuli have an initially unknown temporal structure
of stimulus features of interest, as well as an equally unknown confound structure.
% annotation ftw
In order to evaluate the suitability of the stimulus for the targeted analyses,
and well as to inform the required hemodynamic models, we annotated the temporal
structure of a range of stimulus features.

% AV anno
For the analysis of the movie stimulus, we took advantage of a previously
published annotation of 869 movie cuts and the depicted location after each cut
\citep{haeusler2016cutanno}.
% rationale to use that annotation rationale behind using movie cuts
We conceptualized cuts as events with information on the depicted environment
that require viewers to re-orient themselves within the movie environment by
switching to a new perspective within the same setting, or to a position in an
entirely different setting.
% AV regressors/events
We assigned each cut to one of five categories (Tab.~\ref{tab:events}):
%
1) a cut switching to a setting that was depicted for the first time
(\texttt{vse\_new}),
%
2) a cut switching to a setting that was already depicted earlier in the movie
(\texttt{vse\_old}),
%
3) a cut switching to another locale within a setting (\texttt{vlo\_ch}; e.g. a
cut from first to the second floor in Forrest's house),
%
4) a cut to another camera position within a setting or locale that was depicted
for the first time (\texttt{vpe\_new}), and
%
5) a cut to another camera position within a setting or locale that was already
depicted before (\texttt{vpe\_old}).
% irrespective of visual content
Note that this categorization is not necessarily evident from the visual content
of the first movie frame after a cut.
% cinematographic rationale cut to new scenes: establishing shots
The cinematographic rationale was that movie shots tend to establish the setting
and their spatial layout at their first occurence in a movie.
% cut to recurrent scene
On revisiting an already established setting later in the movie, the field sizes
of movie shots tend to decrease (\texttt{vse\_old}), and shots tend to
more often depict people talking to each other, or objects that are relevant to
the evolved plot (\texttt{vpe\_old}) \citep{brown2012cinematography,
katz1991film, mascelli1998five}.
% neuroscientific rationale The neuroscientific rationale was that activity in
% the PPA is greater when participants view novel versus repeated scenes or
% view-points \citep{epstein1999parahippocampal, grill2006repetition}.  no cut
% condition: intro

As a control condition with events of no particular processing of spatial
information (\texttt{no\_cut}) we pseudo-randomly selected movie frames from
continuous movie shots that lasted longer than \unit[20]{s}, and
% no cuts: how
had a minimum temporal distance of at least \unit[10]{s} to any movie cut and
to any other \texttt{no\_cut} event.

>>>>

% data sources
% https://github.com/psychoinformatics-de/studyforrest-data-aligned/tree/master/code
% https://github.com/psychoinformatics-de/studyforrest-data-templatetransforms}
The current analyses were carried out on previously published fMRI data
(\url{https://github.com/psychoinformatics-de/studyforrest-data-aligned}).
Of those 15 participants in the studyforrest dataset that took
part in all three experiments,
% exclusion of VP 10
data of one participant were dropped to due to invalid distortion correction
during scanning of the audio-description stimulus.
Data were previously corrected for motion, aligned with and re-sliced onto a
participant-specific BOLD template image \citep{sengupta2016extension}
(uniform spatial resolution of \unit[2.5$\times$2.5$\times$2.5]{mm} for both
audio-description and movie data).
% preprocessing intro
Preprocessing was performed by FEAT v6.00 (FMRI Expert Analysis Tool;
\citep{woolrich2001autocorr}) as shipped with
FSL v5.0.9 (\href{https://www.fmrib.ox.ac.uk/fsl}{FMRIB's Software Library};
\citep{smith2004fsl}) on a computer-cluster running
\href{http://neuro.debian.net}{NeuroDebian} \citep{halchenko2012open}.

@@

\todo[inline]{SE: temporal order of the (naturalistic) stimuli is not unknown,
you know it by looking at the movie; COH: yes, but actually no.}

% traditionally
In contrast to stimuli designed to trigger a perceptual process of interest,
while controlling for confounding variables (e.g., color and luminance),
% our approach: annotation and regressors
naturalistic stimuli have fixed but initially unknown temporal structure
of stimulus features of interest, as well as an equally unknown confound structure.
% annotation ftw
In order to evaluate the suitability of the stimulus for the targeted analyses,
and well as to inform the required hemodynamic models, we annotated the temporal
structure of a range of stimulus features.

In an earlier study, \cite{bartels2004mapping} manually annotated the content of
individual movie frames (color, faces, language, and human bodies) and found
that the functional specialization of brain areas is preserved during movie
watching.

% AV anno
For the analysis of the movie stimulus, we took advantage of a previously
published annotation of 869 movie cuts and the depicted location after each cut
\citep{haeusler2016cutanno}.
% we focus on cuts
Contrary to manually annotating stimulus features of every movie frame (as
performed by e.g. \cite{bartels2004mapping} for color, faces, language, and
human bodies), we categorized movie cuts that - in general - realign the viewer
within the movie environment by switching to another perspective within the
same setting, or to a position in an entirely different setting.
% this this should work
More specifically, we sought to exploit a cinematographic bias as
% establishing shots & shots within setting early in the movie
at a setting's first occurrence in a movie, shots tend to broadly establish the
setting and the spatial layout within the setting.
% cut to recurrent scene
On revisiting an already established setting, the field sizes of movie shots
tend to decrease, and shots tend to more often depict people talking to each
other or objects that are relevant to the evolved plot
\citep{brown2012cinematography, katz1991film, mascelli1998five}.

% AV regressors/events
Based on this cinematographic bias, we assigned each cut to one of five
categories (Tab.~\ref{tab:events}):
%
1) a cut switching to a setting that was depicted for the first time
(\texttt{vse\_new}),
%
2) a cut switching to a setting that was already depicted earlier in the movie
(\texttt{vse\_old}),
%
3) a cut switching to another locale within a setting (\texttt{vlo\_ch}; e.g. a
cut from first to the second floor in Forrest's house),
%
4) a cut to another camera position within a setting or locale that was depicted
for the first time (\texttt{vpe\_new}), and
%
5) a cut to another camera position within a setting or locale that was already
depicted before (\texttt{vpe\_old}).
% irrespective of visual content
Note that this categorization is not necessarily evident from the visual content
of the first movie frame after a cut.
% neuroscientific rationale The neuroscientific rationale was that activity in
% the PPA is greater when participants view novel versus repeated scenes or
% view-points \citep{epstein1999parahippocampal, grill2006repetition}.  no cut
% condition: intro
As a control condition with events of no particular processing of spatial
information (\texttt{no\_cut}) we pseudo-randomly selected movie frames from
continuous movie shots that lasted longer than \unit[20]{s}, and
% no cuts: how
had a minimum temporal distance of at least \unit[10]{s} to any movie cut and to
any other \texttt{no\_cut} event.
